Redshift Evolution of the Underlying Type Ia Supernova Stretch Distribution

### 2020-05-19 Nicolas.tex
This is it! 1 column for referee

\documentclass[]{aa}

@@

\usepackage[dvipsnames]{xcolor}

@@

\date{Received 2 November 1992 / Accepted 7 January 1993}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.7\linewidth]{Article_figures/stretchevol_all_vs_snf.pdf}
    \caption{Evolution of the mean SN \textsc{\texttt{SALT2.4}} stretch ($x_1$)
        as a function of redshift. Markers show the mean stretch measured in
        redshift bins of equal sample size, indicated in light gray at the
        bottom of each redshift bins. Full and light markers are used when
        considering the fiducial or the conservative samples, respectively. The
        orange horizontal line represents the mean stretch of the fiducial
        sample, illustrating the expectation if the SN stretch distribution is
        not evolving with redshift. Best fits of our Base drifting model are
        shown as blue, dashed-blue and gray, when fitted on the fiducial sample,
        the conservative one or the SNfactory dataset only, respectively; all
        are compatible. The light-blue band illustrates the amplitude of the
        error (incl. covariance) of the best fit model when considering the
        fiducial dataset. 
        %The redshift distributions of each sample are
        %shown as light-histograms, see lower left legend.
        }
    \label{fig:modelall}
\end{figure*}

@@

        Per Sample Asym. & per sample & 3$\times$5
        & 1468.2 & 1498.2 & $-31.5$
        & 1083.6 & 1113.6 & $-24.1$ 
        \\

@@

Commonly used Malmquist bias correction techniques, such as the BBC-formalism,
assume per Sample Asymmetric Gaussian functions for modeling the underlying
stretch and color distributions. Yet, as shown in Section~\ref{sec:results},
such a sample-based distribution is excluded as being as good as our drifting
model. Then, unlike what \citet[][Section~2]{scolnic2016} and
\citet[][Section~5.4]{scolnic2018a} suggested, i.e. that traditional surveys
span limited redshift ranges and that therefore the per-sample approach accounts
for implicit redshift drifts, a direct modeling of the redshift drift is more
appropriate than a sample-based approach. We stress here that, as measurements
of modern surveys try to cover increasingly larger redshift ranges in order to
reduce calibration systematic uncertainties, this sample-based approach is
becoming less valid, notably for PS1, DES and, soon, LSST.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Article_figures/bbc_comp_PS1_hist-nr.pdf}
    \caption{Distribution of the PS1 SN~Ia \textsc{\texttt{SALT2.4}} stretch
        ($x_1$) after the fiducial redshift limit cut (grey histogram). This
        distribution is supposed to be a random draw from the underlying stretch
        distribution. The green line shows the BBC model of this underlying
        distribution (asymmetric Gaussian). The full line (band) is our best fit
        (its error); the dashed line shows the \cite{scolnic2018a} result. The
        black line (band) show our best fitted Base-modeling (its error, see
        Table \ref{tab:modelresults}) that includes redshift drift. For
        illustration, we show as colored (from blue to red with increasing
        redshifts) the evolution of the underlying stretch distribution as a
        function of redshift for the redshift range covered by PS1 data.}
    \label{fig:bbc_pdf_ps1}
\end{figure}

@@

In the era of modern cosmology, where we aim at probing $w_0$ at a sub-percent
level and $w_a$ at the ten-percent precision \citep[e.g.,][]{lsstpaper}, we
stress that correctly modeling of potential SN redshift drift should be further
studied and care should be made when using samples affected by selection
effects.

@@

In addition to this ``base'' modeling, we have studied various distributions,
including redshift independent models; we also studied the prediction from the
``Beams with Bias Correction'', a Malmquist bias correction algorithm used by
several recent SN~Ia cosmological analyses, implemented as a per-sample
asymmetric Gaussian stretch distribution.

>>>>

\documentclass[referee]{aa}

@@

@@

\date{Submitted to A\&A the 19th of May 2020}

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.7\linewidth]{Article_figures/stretchevol_all_vs_snf.pdf}
    \caption{Evolution of the mean SN \textsc{\texttt{SALT2.4}} stretch ($x_1$)
        as a function of redshift. Markers show the mean stretch measured in
        redshift bins of equal sample size, indicated in light gray at the
        bottom of each redshift bin. Full and light markers are used when
        considering the fiducial or the conservative samples, respectively. The
        orange horizontal line represents the mean stretch of the fiducial
        sample, illustrating the expectation if the SN stretch distribution is
        not evolving with redshift. Best fits of our Base drifting model are
        shown as blue, dashed-blue and gray, when fitted on the fiducial sample,
        the conservative one or the SNfactory dataset only, respectively; all
        are compatible. The light-blue band illustrates the amplitude of the
        error (incl. covariance) of the best fit model when considering the
        fiducial dataset.}
    \label{fig:modelall}
\end{figure*}

@@

        Per sample Asym. & per sample & 3$\times$5
        & 1468.2 & 1498.2 & $-31.5$
        & 1083.6 & 1113.6 & $-24.1$ 
        \\

@@

Commonly used Malmquist bias correction techniques, such as the BBC-formalism,
assume per sample asymmetric Gaussian functions for modeling the underlying
stretch and color distributions. Yet, as shown in Section~\ref{sec:results},
such a sample-based distribution is excluded as being as good as our drifting
model. Then, unlike what \citet[][Section~2]{scolnic2016} and
\citet[][Section~5.4]{scolnic2018a} suggested, i.e. that traditional surveys
span limited redshift ranges and that therefore the per-sample approach accounts
for implicit redshift drifts, a direct modeling of the redshift drift is more
appropriate than a sample-based approach. We stress here that, as measurements
of modern surveys try to cover increasingly larger redshift ranges in order to
reduce calibration systematic uncertainties, this sample-based approach is
becoming less valid, notably for PS1, DES and, soon, LSST.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{Article_figures/bbc_comp_PS1_hist-nr.pdf}
    \caption{Distribution of the PS1 SN~Ia \textsc{\texttt{SALT2.4}} stretch
        ($x_1$) after the fiducial redshift limit cut (grey histogram). This
        distribution is supposed to be a random draw from the underlying stretch
        distribution. The green lines show the BBC model of this underlying
        distribution (asymmetric Gaussian). The full line (band) is our best fit
        (its error); the dashed line shows the \cite{scolnic2018a} result. The
        black line (band) shows our best fitted Base-modeling (its error, see
        Table \ref{tab:modelresults}) that includes redshift drift. For
        illustration, we show as colored (from blue to red with increasing
        redshifts) the evolution of the underlying stretch distribution as a
        function of redshift for the redshift range covered by PS1 data.}
    \label{fig:bbc_pdf_ps1}
\end{figure}

@@

In the era of modern cosmology, where we aim at probing $w_0$ at a sub-percent
level and $w_a$ at the ten-percent precision \citep[e.g.,][]{lsstpaper}, we
stress that correct modeling of potential SN redshift drift should be further
studied and care should be taken when using samples affected by selection
effects.

@@

In addition to this ``base'' modeling, we have studied various distributions,
including redshift independent models; we also studied the prediction from a per-sample asymmetric Gaussian stretch distribution used, for instance, by the Beams with Bias Correction Malmquist bias correction algorithm \citep{scolnic2016, kessler2017}.
